\documentclass[a4paper, twoside]{IEEEtran}
\IEEEoverridecommandlockouts

% Dokumentation IEEEtran LaTeX class
% https://ras.papercept.net/conferences/support/files/IEEEtran_HOWTO.pdf

\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage[noadjust]{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{balance}
\usepackage{float}
\usepackage[all]{nowidow}
\usepackage{listings}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage[capitalise]{cleveref}
\usepackage{booktabs}
\usepackage{makecell}

\lstdefinestyle{python}{
    language=Python,
    escapechar=!,
    captionpos=b,
    basicstyle=\small\ttfamily,
    keywordstyle=\color{blue},
    stringstyle=\color{red},
    commentstyle=\color{gray},
    breaklines=true
}

% don't judge
\hbadness=10000

% group citations
\renewcommand{\citepunct}{,\penalty\citepunctpenalty\,}
\renewcommand{\citedash}{--}

\begin{document}

\title{Project Report—CoDes: Co-Design of Serverless Platforms and Applications}

\author{
    \IEEEauthorblockN{
        Valentin Carl\IEEEauthorrefmark{1},
        Daniel Gottschling\IEEEauthorrefmark{2},
        Jonas Heisterberg\IEEEauthorrefmark{2},
        David Schmidt\IEEEauthorrefmark{2}, and
        Marvin Steinke\IEEEauthorrefmark{1}
    }\\
    \IEEEauthorblockA{
        Technische Universität Berlin\\
        Email:
        \IEEEauthorrefmark{1}\{carl, marvin.steinke\}@tu-berlin.de,
        \IEEEauthorrefmark{2}\{d.gottschling, heisterberg, d.schmidt\}@campus.tu-berlin.de
    }
}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}

    Serverless cloud computing, such as Function-as-a-Service (FaaS), offers
    operational benefits for large-scale applications. These include enhanced
    developer productivity and cost-efficiency. However, there are challenges
    such as double billing, cascading cold starts, and added latency due to
    inefficient scheduling of function calls. This project focuses on
    integrating three potential solutions - \textsc{Fusionize}, SAND, and
    \textsc{ProFaaStinate} into the open-source serverless platform Nuclio.
    \textsc{Fusionize} reduces remote call overheads and prevents cold start
    cascades by using function fusion. SAND uses application-level sandboxing
    and a hierarchical message bus for efficient cloud resource usage and
    latency reduction. \textsc{ProFaaStinate} tries to efficiently manage
    resource utilization by delaying the execution of function calls. However,
    implementing these solutions within Nuclio has exposed some limitations,
    mainly because of the platform's instability and the restrictions posed by
    container orchestration systems which are not specifically tailored for FaaS
    applications like Kubernetes. For these optimization techniques to work
    effectively, they need to be integrated within platforms explicitly designed
    to accommodate them.

\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\input{sections/1_introduction}
\input{sections/2_nuclio}
\input{sections/3_fusionize}
\input{sections/4_sand}
\input{sections/5_profaastinate}
\input{sections/6_evaluation}
\input{sections/7_discussion}
\input{sections/8_conclusion}

%\balance

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\section*{Author Attribution}

% Usage: Name & \ref{sec:section} \\

\vspace{1em}
\begin{center}
    \begin{tabular}{l l} \toprule
        Name & Sections \\ \midrule
        Valentin Carl &
            \ref{sec:sand},
            \ref{subsubsec:evaluation:fusionize_and_sand:results},
            \ref{sec:discussion},
            \\
        Daniel Gottschling &
            \ref{sec:sand},
            \ref{subsubsec:evaluation:fusionize_and_sand:results},
            \\
        Jonas Heisterberg & \\
        David Schmidt & \\
        Marvin Steinke & \makecell[l]{
            Abstract,
            \ref{sec:introduction},
            \ref{sec:fusionize},
            \ref{sec:evaluation}-intro, \\
            \ref{subsubsec:evaluation:fusionize_and_sand:experiment_setup},
            \ref{subsubsec:discussion:interpretation_of_experiment_results:fusionize_and_sand},
            \ref{sec:conclusion}
        }\\ \bottomrule
    \end{tabular}
\end{center}

\end{document}
