\section{Evaluation}\label{sec:evaluation}

In this section, we evaluate and compare the performance of our implementations of Fusionize, SAND, and ProFaaStinate.

\subsection{Fusionize and SAND}

%
% <TODO>
%

\paragraph{Experiment Setup}

for fusionize and sand we designed a benchmark aimed at isolating the network overhead to simulate cascading cold starts and double billing.
we chose method best showcases end to end latencies between FaaS functions. 
we decided for synthetic base load to investigate system's performance under maximum stress.
                                                                               
To showcase maximum latency, we designed two tasks, shown in Figure X, \emph{interface} task and \emph{counter} task. 
The counter Task receives a number and returns the number, incremented by one. 
The interface task receives a \emph{destination} number by the user and invokes the counter task, starting with the number zero. 
The result of the counter task is then used to invoke the counter task again until the destination number is reached.
                                                                               
This proposed load generator is unconventional, as it resides within the system under test. 
However, this design allows for function invocation within the platfrom and most importantly \emph{between} functions. 
To start the benchmark, only the interface task needs to be invoked with destination number and latency between invocation and result is to measured.

%
% </TODO>
%

\paragraph{Results}

In figure~\ref{fig:sand_fusionize}, we can see the results of our benchmark. 
The x-axis shows the number of function calls required the answer the request, and the y-axis show the measured end-to-end latency.
As the interaction between functions increases, the end-to-end latency increases linearly for SAND. 
With 10,000 function calls, the SUT takes approximately 50 seconds to answer the request using our SAND implementation.
For vanilla Nuclio, the latency caused by the same request if significantly lower at below 20 seconds.
The end-to-end latency of vanilla Nuclio scales exponentially with increasing interaction between functions.
With Fusionize, the latency is very close to 0 throughout the experiment.

\subsection{ProFaaStinate}

%
% TODO
%

\textbf{TODO}
